Benchmarking

### 2023-08-09 Misc/benchmarks.qmd
sync changes

>>>>

```{r}
pacman::p_load(tidyverse,tidybayes,brms,broom,broom.mixed,lme4,here,knitr,gt,gghalves,patchwork,ggdist,microbenchmark)
e1 <- readRDS(here("data/e1_08-04-23.rds"))
test <- e1 |> filter(expMode2 == "Test")  
options(mc.cores = 4, brms.backend = "cmdstanr",brms.silent=0)

gprior<- c( prior(normal(800, 100), class = Intercept),
    prior(normal(400, 10), class = sigma)
  )

tf <- system.time(
fit_int_norm <- brm(vx ~ 1, 
  data = test,
  family = gaussian(),
  prior = gprior,
  silent=0
)
)
tf

tf2 <- system.time(
fit_int_norm <- brm(vx ~ 1 +(1|bandInt) + (1|id),
  data = test |> filter(id %in% 1:15),
  family = gaussian(),
  prior = gprior
)
)
tf2

cat(paste0("brms int only gaussian=",round(tf["elapsed"],2)," \n ",
          # "foreach parallel time=",round(tfP["elapsed"],2)," \n ",
           "irt version= ",round(tf2["elapsed"],2)
          ))
